\CRANpkg{lg}: An R package for Local Gaussian Approximations

### 2021-02-16 otneim.tex
Revised conclusion

The statistical literature has seen a number of applications of local Gaussian approximations in the last decade, covering several topics in dependence modeling and inference, as well as the estimation of multivariate density and conditional density functions. In this paper, we demonstrate the implementation of these methods i the R programming language using the \CRANpkg{lg}-package, as well as the graphical representation of the estimated local Gaussian correlation. The package is complete, in the sense that all major methods that have been published within this framework is now easily accessible to the practitioner. The package is also modular; Future methodological developments using local Gaussian approximations may be added to the package with little effort.

>>>>

The statistical literature has seen a number of applications of local Gaussian approximations in the last decade, covering several topics in dependence modeling and inference, as well as the estimation of multivariate density and conditional density functions. In this paper, we demonstrate the implementation of these methods i the R programming language using the \CRANpkg{lg}-package, as well as the graphical representation of the estimated local Gaussian correlation. The package is complete, in the sense that all major methods that have been published within this framework is now easily accessible to the practitioner. The package is also designed with a modular infrastructure that allows future methodological developments using local Gaussian approximations to be added to the package.
